{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-08-31 wacv_for_review.tex
Updated Figure Order
Burak Final Commits

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems already come with an image acquisition
pipeline, and a tremendous amount of progresses on research has been
made for many areas in computer vision. However, to successfully
deploy a computer vision algorithm on any existing embedded systems, a
vision algorithm needs to satisfy, at least, two criteria with
assumption of reasonably good performance: minimal, manual
intervention after deployment and small footprint of consuming
computational resources and executable code. To develop a single,
target tracking system in high accuracy and run-time performance while
these criteria kept in mind, we propose an ensemble of the kernelized
correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
is specifically designed to address the scale-change and dynamic
maneuver of the target over frames. In particular, to guarantee a
high-speed, run-time performance, we deploy each of KCFs in turn and assign 
them hand-crafted features including histogram of oriented gradients and color features.
For a smooth transition between individual KCFs' executions, we developed
a Bayes filter. Experimental results showed that the performance of
ours are, on average, 70.10\% for precision at 20 pixels, 53.00\% for
success rate for OTB100 data, and 54.50\% and 40.2\% for UAV123
data. These results showed that our method is better than existing
ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
average. Moreover our implementation ran at 340 fps for OTB100 and at
416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
and KCF (292 fps), DCF (457 fps) for UAV123. Finally, for the embedded
systems with GPUs, we explored different levels of deep features for different
correlation filters to boost tracking performance. 
\end{abstract}

@@

The contribution of this study is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps that deploys an
ensemble of KCFs, in turn, to more effectively address the scale
variance and the dynamic maneuver of a target while preserving
run-time performance as high as possible. To minimize any potential
performance gap from transiting one KCF to another, we use a Bayes
filter.

@@

\textbf{{\it E}nKCF with Hand-crafted Features}
We, first, explore traditional features to run  {\it E}nKCF on any embedded system as it is the primary
objective of this study. In this direction, we employ two highly efficient features; fHoG \cite{felzenszwalb2010object}
and color-naming \cite{li2014scale}. Figure \ref{fig:Filters} shows examples of the region of interest (ROI) associated with $R_{t}^{S}$,
$R_{t}^{L}$, and $R_{s}$ assigned hand-crafted features, . This version of {\it E}nKCF is dedicated to run
on any embedded system at real-time ($30$fps).

\textbf{{\it E}nKCF with Convolutional Neural Network Features}
In addition to hand-crafted featurres, we explore deep features
to boost tracking performance. This version of {\it E}nKCF, on the other hand, 
is dedicated to run on high-end embedded systems (GPUs).

There have been many studies on applying a pretrained CNN features to
tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer features of the VGGNet
\cite{simonyan2014very} for this idea where their experiments showed
that the first convolutional layer features lead to slightly better
precision and success rates than the second
layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper
features. Their method employs the third convolutional layer features
to get the response map. In the next stage, they used the estimation
of the target's transition from the first stage to use the second
convolutional layer features. Finally, the first convolutional layer
features is extracted from the position estimated in the second
stage. This coarse-to-fine position estimation approach allows to
utilize more representative features of the object. However, such
approach requires multiple runs of a KCF at a single frame, increasing
the run-time complexity. For this reason, we follow a similar approach
to \cite{danelljan2015convolutional} to embed deep learning features.

Our {\it E}nKCF framework provides us with a flexibility to exploit different
level of abstractions in different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, considers more than twice bigger area
than $R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it requires less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment is represented as \textit{conv224-VGG} and shown in
fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
resolution at the first layers than than AlexNet
\cite{krizhevsky2012imagenet}.

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction framework to use deep features in {\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target boundary information loss.}
\label{fig:Filters_CNN}
\end{figure}

\textbf{Kernelized Correlation Filter} The Kernelized Correlation
Filter is a well, known single target tracking method and its work
flow has been detailed in other papers
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the correlation filter
framework representing training examples as a circulant matrix. The
fact that a circulant matrix can be diagonalized by Discrete Fourier
transform is the key to reduce the complexity of any tracking method
based on correlation filter. The off-diagonal elements become zero
whereas the diagonal elements represent the eigenvalues of the
circulant matrix. The egienvalues are equal to the DFT transformation
of the base sample ($x$) elements. The Kernelized Correlation Filter,
in particular, applies a kernel to $x$ to transform to a more
discriminative domain. The circulant matrix is then formed by applying
cyclic shifts on the kernelized $x$. Such kernelization operation
maintains O($nlog(n)$) complexity unlike other kernel algorithms
leading to O($n^{2}$) or even higher complexities.

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To evaluate the performance of the proposed  {\it
  E}nKCF with hand-crafted features, we choose two
publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 data is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 data, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 data that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, we call it
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

\begin{figure*}[h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\hspace{.37\linewidth}\textbf{OTB100}\\
\includegraphics[width=3.30cm]{./figures/pr_uav123.eps}
\includegraphics[width=3.55cm]{./figures/sr_uav123.eps}
\includegraphics[width=3.30cm]{./figures/pr_otb100.eps}
\includegraphics[width=3.55cm]{./figures/sr_otb100.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure*}

\textbf{Features Selections} We used different features for each of
three KCFs as each of them has different goals to accomplish. In
particular, the translation filter, $R_{t}^{L}$, uses both the fast
Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
and color-naming \cite{van2009learning} features to more effectively
learn the background around the target as shown in figure~\ref{fig:Filters}. 
Through experiments, we found that only fHoG didn't work well to cover a larger ROI; another
translation filter, $R_{t}^{S}$, worked well when it used fHoG
features only; the scale filter, $R_{s}$ did when it used both fHoG
and color features.

@@

@@

For the $UAV123$ dataset, we also evaluated the performance of the
{\it E}nKCF with and without the particle filter. In particular, we
use 50 sequences labeled as no abrupt camera motion in the dataset. To
evaluate the robustness of particle filter, we add noise, drawn from a
uniform distribution ($[-20,20]$), to the translation estimations of
the KCFs. In these setup, the {\it E}nKCF with particle filter
achieves $51.98\%$ precision ($20$px), outperforming the one without
particle filter {\it E}nKCF by $6.32\%$. Thus, with the removal of
global camera motion, the integration of particle filter into the {\it
  E}nKCF as shown in Figure \ref{Workflows} further improved the
results.

@@

\begin{table*}[h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset. This table empirically supported the usefulness of
  combining multiple KCFs as long as the deployment order is optimal.}
\label{table:Comparison_to_LCT}
\end{table*}

@@

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
  dataset where the original UAV123 data was temporally downsampled.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used HoG and color features in an
efficient way for the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. We hypothesize that the {\it E}nKCF
tracker could perform better with deep features trained on ImageNet
dataset. Utilizing pretrained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. But as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ conv features as shown in figure~\ref{fig:Filters_CNN}.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
results of utilizing DNN features on UAV123 Dataset. Two settings of utilizing the deep
features outperformed the HoG and color features as proposed in {\it
  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
success rates (AUC). The \textit{conv224-VGG} setting performed
slightly better than \textit{conv222-VGG} in precision while achieving
similar success rate (AUC).

\begin{figure}[t]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems already come with an image acquisition
pipeline, and a tremendous amount of progresses on research has been
made for many areas in computer vision. However, to successfully
deploy a computer vision algorithm on any existing embedded systems, a
vision algorithm needs to satisfy, at least, two criteria with
assumption of reasonably good performance: minimal, manual
intervention after deployment and small footprint of consuming
computational resources and executable code. To develop a single,
target tracking system in high accuracy and run-time performance while
these criteria kept in mind, we propose an ensemble of the kernelized
correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
is specifically designed to address the scale-change and dynamic
maneuver of the target over frames. In particular, to guarantee a
high-speed, run-time performance, we deploy each of KCFs in turn and assign 
them hand-crafted features including histogram of oriented gradients and color features.
For a smooth transition between individual KCFs' executions, we developed
a Bayes filter. Experimental results showed that the performance of
ours are, on average, 70.10\% for precision at 20 pixels, 53.00\% for
success rate for OTB100 data, and 54.50\% and 40.2\% for UAV123
data. These results showed that our method is better than existing
ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
average. Moreover our implementation ran at 340 fps for OTB100 and at
416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
and KCF (292 fps), DCF (457 fps) for UAV123. Finally, dedicated for the embedded
systems with GPUs, we explored different levels of deep features for different
correlation filters to boost tracking performance and call it Deep{\it E}nKCF. 
\end{abstract}

@@

The contribution of this study is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps that deploys an
ensemble of KCFs, in turn, to more effectively address the scale
variance and the dynamic maneuver of a target while preserving
run-time performance as high as possible. To minimize any potential
performance gap from transiting one KCF to another, we use a Bayes
filter. Finally, we explore deep features with varying levels of abstraction
in the proposed {\it E}nKCF to improve tracking performance.

@@

\textbf{{\it E}nKCF with Hand-crafted Features}
We, first, explore traditional features to run  {\it E}nKCF on any embedded system as it is the primary
objective of this study. In this direction, we employ two highly efficient features; fHoG \cite{felzenszwalb2010object}
and color-naming \cite{li2014scale}. Figure \ref{fig:Filters} shows examples of the region of interest (ROI) associated with $R_{t}^{S}$,
$R_{t}^{L}$, and $R_{s}$. This version of {\it E}nKCF is dedicated to run
on any embedded system at real-time ($30$fps).

We used different features for each of three KCFs as each of them 
has different goals to accomplish. In particular, the translation filter, $R_{t}^{L}$, 
uses both the fHoG \cite{felzenszwalb2010object}
and color-naming \cite{van2009learning} features to more effectively
learn the large background area around the target as shown in figure~\ref{fig:Filters}. The color features
compensate for the noisier shape features due to the large ROI considered by $R_{t}^{L}$.
On the other hand, color features is not assigned to $R_{t}^{S}$ as it learns more useful shape
features than $R_{t}^{L}$ due to smaller padding size. Finally, $R_{s}$ is assigned both fHoG 
and color-naming features since we believe that the lower template resolution (64 x n) assigned to
$R_{s}$ might lead to less discriminative shape features. Smaller template size is assigned to 
$R_{s}$ as it estimates the scale by correlating the filter with three ROIs as shown in alg.~\ref{alg:MKCF}. 
This way, we can keep the run-time complexity of the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that 
only run correlation filter on a single ROI. By doing so, we can avoid fluctuating run-time performance 
which is not desired in embedded systems.
%Through experiments, we found that only fHoG didn't work well 
%to cover a larger ROI; another translation filter, $R_{t}^{S}$, worked well when it used fHoG
%features only; the scale filter, $R_{s}$ did when it used both fHoG
%and color features.

\textbf{{\it E}nKCF with Convolutional Neural Network Features}
In addition to hand-crafted features, we explore deep features
to boost tracking performance. This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, 
is dedicated to run on high-end embedded systems (GPUs).

There have been large volume of stuides on utilizing a pre-trained CNN features to
tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer features of the VGGNet
\cite{simonyan2014very} for this idea where their experiments showed
that the first convolutional layer features lead to slightly better
precision and success rates than the second
layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper
features. Their method employs the third convolutional layer features
to estimate the response map. In the next stage, they used the estimation
of the target's transition from the first phase to use the second
convolutional layer features and update transition estimation. 
Finally, the first convolutional layer features is extracted from the ROI estimated 
in the second stage. This coarse-to-fine position estimation approach accommodates
different levels of abstractions of the object. However, such
approach runs multiple KCFs at a single frame, increasing
the run-time complexity. For this reason, we follow a similar approach
to \cite{danelljan2015convolutional} to embed deep features in {\it E}nKCF.

Our {\it E}nKCF framework allows us to exploit different
level of feature encodings in different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, considers at least twice bigger area
than $R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it relies on less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment scheme is represented as \textit{conv224-VGG} and shown in
fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
resolution at the first layers than AlexNet
\cite{krizhevsky2012imagenet}.

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
\label{fig:Filters_CNN}
\end{figure}

\textbf{Kernelized Correlation Filter} The Kernelized Correlation
Filter is a well-known single target tracking method and its work
flow has been detailed in other papers
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the correlation filter
framework representing training examples as a circulant matrix. The
fact that a circulant matrix can be diagonalized by Discrete Fourier
transform is the key to reduce the complexity of any tracking method
based on correlation filter. The off-diagonal elements become zero
whereas the diagonal elements represent the eigenvalues of the
circulant matrix. The egienvalues are equal to the DFT transformation
of the base sample ($x$) elements. The Kernelized Correlation Filter,
in particular, applies a kernel to $x$ to transform to a more
discriminative domain. The circulant matrix is then formed by applying
cyclic shifts on the kernelized $x$. Such kernelization operation
maintains O($nlog(n)$) complexity unlike other kernel algorithms
leading to O($n^{2}$) or even higher complexities.

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We first evaluate the performance of {\it E}nKCF with hand-crafted features.
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

\begin{figure*}[h]
\centering
\begin{tabular}{ccc}
\tiny\quad\textbf{UAV123}\hspace{.37\linewidth}\textbf{OTB100}\\
\includegraphics[width=3.30cm]{./figures/pr_uav123.eps}
\includegraphics[width=3.55cm]{./figures/sr_uav123.eps}
\includegraphics[width=3.30cm]{./figures/pr_otb100.eps}
\includegraphics[width=3.55cm]{./figures/sr_otb100.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure*}

%\textbf{Features Selections} We used different features for each of
%three KCFs as each of them has different goals to accomplish. In
%particular, the translation filter, $R_{t}^{L}$, uses both the fast
%Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
%and color-naming \cite{van2009learning} features to more effectively
%learn the background around the target as shown in figure~\ref{fig:Filters}. 
%Through experiments, we found that only fHoG didn't work well to cover a larger ROI; another
%translation filter, $R_{t}^{S}$, worked well when it used fHoG
%features only; the scale filter, $R_{s}$ did when it used both fHoG
%and color features.

@@

\begin{table*}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset. This table empirically supported the usefulness of
  combining multiple KCFs as long as the deployment order is optimal.}
\label{table:Comparison_to_LCT}
\end{table*}

@@

\textbf{Evalution on Particle Filter Contribution} For the $UAV123$ dataset, we also evaluated the performance of the
{\it E}nKCF with and without the particle filter. In particular, we
use 50 sequences labeled as no abrupt camera motion in the dataset. To
evaluate the robustness of particle filter, we add noise, drawn from a
uniform distribution ($[-20,20]$), to the translation estimations of
the KCFs. In these setup, the {\it E}nKCF with particle filter
achieves $51.98\%$ precision ($20$px), outperforming the one without
particle filter {\it E}nKCF by $6.32\%$. Thus, with the removal of
global camera motion, the integration of particle filter into the {\it
  E}nKCF as shown in Figure \ref{Workflows} further improved the
results.

@@

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\tiny\quad\textbf{UAV123$\_$10fps}\\
\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
  dataset where the original UAV123 data was temporally downsampled.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used fHoG and color-naming features in an
efficient way for the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. Following the recent trend, we hypothesize 
that the {\it E}nKCF tracker could be improved with deep features trained on ImageNet
dataset. Utilizing pre-trained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. However, as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) as shown in figure~\ref{fig:Filters_CNN}.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
results of utilizing DNN features on UAV123 Dataset. Two settings of utilizing the deep
features outperformed the HoG and color features as proposed in {\it
  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
success rates (AUC). The \textit{conv224-VGG} setting performed
slightly better than \textit{conv222-VGG} in precision while achieving
similar success rate (AUC) indicating that higher level feature absractions 
works better for the smaller ROIs.
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's ({\it hog} + {\it color}) performance with Deep{\it E}nKCF on the UAV123
dataset.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}
